\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 results.tex
Corrected missed references
corrected a typo

A significant driver of the applicability of our work was the
implementation of MBARI's \emph{Gulper} water-samplers \cite{Bird07},
$2$ litre syringe style containers $10$ of which are encased within
the mid-body section of our Dorado vehicle as shown in Fig
\ref{fig:gulper}. However, the original design and intended use of
operation continued to dominated by a naive belief of collecting and
returning water samples as traditional ship-borne methods often
employ, namely using pre-scripted methods, albeit on a highly capable
robot. With the installation of \rx onboard the Dorado with its
capability to synthesize plans and replan on the fly, more imaginative
methods of sample acquisition were targeted.

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.pdf}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

To augment our understanding of such microbial communities, the Dorado
with \rx has been utilized in a range of activities in a
quasi-lagrangian mode. As the water mass is being tracked with a
drifting instrument, the vehicle is expected to move around it. While
a number of different patterns have been tested in simulation, the
majority of at-sea deployments have used a square pattern ($3X3$
km\textsuperscript{2} or a $1X1$ km\textsuperscript{2})\footnote{Often
  post-hoc reconstruction of the data set for visualization drives how
  much adaptation the vehicle can be allowed to undertake.}. Plan
synthesis occurs frequently, but within the context of a drifting
point generated by a drifter. Fig. \ref{fig:dta-setup} shows the
general setup of our experiments which can be tailored with the use of
various computational methods within the \texttt{DTA} app which is
contained within the Oceanographic Decision Support System (\od; see
below) \cite{das11}. GPS data from the free-floating drifter is sent
via satellite and processed onshore to determine a projection (speed
and bearing) of the drifter. This data is sent to the AUV; at the
completion of the current survey, the vehicle receives this data as a
high-level goal which is decomposed and synthesized as a survey
plan. Currently, the vehicle completes the survey without any further
dynamic updates from the drifter. In order to minimize the range of
errors that the survey needs to encapsulate (data latency or surface
or sub-surface currents for those drifters which have a drogue) the
estimation is a projection in time and space of the drifters centroid
sent with this goal from the shore-side app.

@@

\begin{figure}[htpb]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows red track lines of the \rx commanded
  Dorado with the yellow transects of the LRAUV. Yellow dots show the
  track line of a simple GPS-enabled drifter used for seeding the
  experiment over the Monterey Canyon with Santa Cruz, CA to the right
  of the figure.}
\label{fig:ballet}
\end{figure}

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{sep11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rxe. We are
currently investigating spatio-temporal correlations \cite{gneiting07}
of CTD data obtained by the \texttt{Wirewalker} and tying it to the
observations made in the contextual environment by the Dorado's
sensors.

@@

\begin{figure*}
\centering
\subfloat[The \od Concept]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
\subfloat[Current Implementation for \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small Fig. \ref{fig:odss-mtg} shows a 2010 \can meeting with
  the \od in use. Fig. \ref{fig:odss-virtual} shows a drifter tracking
  tool used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. Fig. \ref{fig:odss-ipad} shows \od use on a portable
  iPad device.}
\label{fig:odss2}
\end{figure*}

>>>>

A significant driver of the applicability of our work was the
growing need for AUVs mission to be driven by scientific sensor 
data.This trend is illustrated by the 
implementation of MBARI's \emph{Gulper} water-samplers \cite{Bird07},
$2$ litre syringe style containers $10$ of which are encased within
the mid-body section of our Dorado vehicle as shown in Fig
\ref{fig:gulper}. However, the original design and intended use of
operation continued to dominated by a naive belief of collecting and
returning water samples as traditional ship-borne methods often
employ, namely using pre-scripted methods, albeit on a highly capable
robot. With the installation of \rx onboard the Dorado with its
capability to synthesize plans and replan on the fly, more imaginative
methods of sample acquisition were targeted.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{figs/dta-app.pdf}
\caption{\small{Overall setup of \can lagrangian experiments with a
    drifting instrument pack. Various combinations of computational
    methods can be included in the Drifter Tracking App which is a
    part of the Oceanographic Decision Support System (\od)
    \cite{das11}.}}
\label{fig:dta-setup}
\end{figure}

To augment our understanding of such microbial communities, the Dorado
with \rx has been utilized in a range of activities in a
quasi-lagrangian mode. As the water mass is being tracked with a
drifting instrument, the vehicle is expected to move around it. While
our model suppirt multiples patterns(square, lawn-mower,
transect(s)\dots) with any possible dimension factor, the
majority of at-sea deployments have used a square pattern ($3X3$
km\textsuperscript{2} or a $1X1$ km\textsuperscript{2})\footnote{Often
  post-hoc reconstruction of the data set for visualization drives how
  much adaptation the vehicle can be allowed to undertake.}. Plan
synthesis occurs frequently, but within the context of a drifting
point generated by a drifter. Fig. \ref{fig:dta-setup} shows the
general setup of our experiments which can be tailored with the use of
various computational methods within the \texttt{DTA} app which is
contained within the Oceanographic Decision Support System (\od; see
below) \cite{das11}. GPS data from the free-floating drifter is sent
via satellite and processed onshore to determine a projection (speed
and bearing) of the drifter. This data is sent to the AUV; at the
completion of the current survey, the vehicle receives this data as a
high-level goal which is decomposed and synthesized as a survey
plan. Currently, the vehicle completes the survey without any further
dynamic updates from the drifter. In order to minimize the range of
errors that the survey needs to encapsulate (data latency or surface
or sub-surface currents for those drifters which have a drogue) the
estimation is a projection in time and space of the drifters centroid
sent with this goal from the shore-side app.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{figs/oct10-ballet.pdf}
\caption{\small An October 2010 robot ``ballet'' where a smaller
  slower AUV tracked a patch center, sending periodic updates to the
  Dorado using a setup shown in Fig. \ref{fig:dta-setup}. The Google
  Earth post-hoc image shows {\color{red}red} track lines of the \rx
  commanded Dorado with the {\color{yellow}yellow} transects of the
  LRAUV. {\color{yellow}Yellow} dots show the track line of a
  GPS-enabled drifter used for seeding the experiment over the
  Monterey Canyon with Santa Cruz, California to the right of the
  figure.}
\label{fig:ballet}
\end{figure}

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{fig:sept11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rxe. We are
currently investigating spatio-temporal correlations \cite{gneiting07}
of CTD data obtained by the \texttt{Wirewalker} and tying it to the
observations made in the contextual environment by the Dorado's
sensors.

@@

\begin{figure*}
  \centering
  \subfloat[A conceptual view of the \od and how it fits into \can
  field experiments]{\label{fig:odss-concept}\includegraphics[width=0.5\textwidth]{figs/odss-concept.pdf}}\\
  \subfloat[Current implementation of \od for
  \can]{\label{fig:odss-frontend}\includegraphics[width=0.5\textwidth]{figs/dss-screenshot.png}}
\caption{\small The Oceanographic Decision Support System (\od) is a
  single portal for planning, visualization, situational awareness,
  collaboration and archival of information before, during and after
  field experiments. The \od has been used since mid-year 2010 for
  \can field experiments.}
\label{fig:odss}
\end{figure*}

@@

\begin{figure*}
\centering
\subfloat[]{\label{fig:odss-mtg}\includegraphics[width=0.3\textwidth]{figs/october-canon-meeting.png}}
\subfloat[]{\label{fig:odss-virtual}\includegraphics[width=0.33\textwidth]{figs/virtual-drifter-tool.png}}
\subfloat[]{\label{fig:odss-ipad}\includegraphics[width=0.3\textwidth]{figs/photo-ipad-2.jpg}}
\caption{\small \ref{fig:odss-mtg} shows a 2010 \can meeting with the
  \od in use. \ref{fig:odss-virtual} shows a drifter tracking tool
  used during \can planning; it used a physical model of advected
  surface currents from \texttt{CeNCOOS} \cite{cencoos} to plan AUV
  deployments. \ref{fig:odss-ipad} shows \od use on an iPad.}
\label{fig:odss2}
\end{figure*}
